Reply to: 2022-05603 Intentional release of native species undermines ecological stability

### 2022-10-22 rmd/supporting_info.Rmd
text{max}

```{=tex}
\begin{align}
N_{i,t+1} = (N_{i,t}+\phi_i R_t) ~ \exp \left[r_i \left(1-\frac{\alpha_{i1}R_t + \sum_{j=1}^S \alpha_{ij}N_{j,t}}{K_i} \right) \right]\exp(\varepsilon_{i,t})
\end{align}
```
In this model, intrinsic growth rates of unenhanced species $r_{i,i \ne 1}$ and interspecific competition $\alpha_{ij}$ are random draws from a uniform ($r_{i,i \ne 1} \sim \text{Unif}(0.5,r_{max})$) and an exponential distribution ($\alpha_{ij} \sim \text{Exp}(1/\bar{\alpha})$), respectively. We assumed constant values of intraspecific competition ($\alpha_{ii}=1$), carrying capacity $(K_i = K)$ and the number of releases $(R_t=R)$.

@@

We subsequently analyzed a whole community model with 10 species using important parameter combinations identified in the two-species simulation: intrinsic growth of enhanced species ($r_1 =$ `r unique(list_param[[2]]$r1)`), average strength of interspecific competition ($\bar{\alpha}=$ `r unique(list_param[[2]]$alpha)`), carrying capacity ($K=$ `r unique(list_param[[2]]$k)`). We also varied relative fitness of captive-bred individuals ($f_R=$ `r unique(list_param[[2]]$phi)`) as this is a common interest in captive-breeding programs. Meanwhile, we fixed values of the following parameters: the number of species ($S=$ `r unique(list_param[[2]]$n_species)`), maximum intrinsic growth rate of unenhanced species ($r_{max}=$ `r unique(list_param[[2]]$r_max)`), and environmental stochasticity ($\sigma_{\varepsilon}=$ `r unique(list_param[[2]]$sd_env)`). This simulation setup resulted in `r nrow(list_param[[2]])` sets of parameter combinations.

@@

  cap[i] <- paste0("Theoretical predictions for the release effect in a ten-species community. Rows represent different response variables, and columns show distinct simulation scenarios with different strengths of interspecific competition ($\\bar{\\alpha}$) and relative fitness of captive-bred individuals ($f_R$). Lines are loess curves (mean) with shades indicating associated 95% confidence intervals. Other parameters are: ",
                       "number of species $S$ = ", df_param$n_species[i], "; intrinsic growth rate of an enhanced species $r_1$ = ", df_param$r1[i], "; maximum intrinsic growth rate of unenhanced species $r_{max}$ = ", df_param$r_max[i], "; environmental stochasticity $\\sigma_{\\varepsilon}$ = ", df_param$sd_env[i], "; carrying capacity $K$ = ", df_param$k[i], ".")

>>>>

```{=tex}
\begin{align}
N_{i,t+1} = (N_{i,t}+\phi_i R_t) ~ \exp \left[r_i \left(1-\frac{\alpha_{i1}R_t + \sum_{j=1}^S \alpha_{ij}N_{j,t}}{K_i} \right) \right]\exp(\varepsilon_{i,t})
\end{align}
```
In this model, intrinsic growth rates of unenhanced species $r_{i,i \ne 1}$ and interspecific competition $\alpha_{ij}$ are random draws from a uniform ($r_{i,i \ne 1} \sim \text{Unif}(0.5,r_{\text{max}})$) and an exponential distribution ($\alpha_{ij} \sim \text{Exp}(1/\bar{\alpha})$), respectively. We assumed constant values of intraspecific competition ($\alpha_{ii}=1$), carrying capacity $(K_i = K)$ and the number of releases $(R_t=R)$.

@@

We subsequently analyzed a whole community model with 10 species using important parameter combinations identified in the two-species simulation: intrinsic growth of enhanced species ($r_1 =$ `r unique(list_param[[2]]$r1)`), average strength of interspecific competition ($\bar{\alpha}=$ `r unique(list_param[[2]]$alpha)`), carrying capacity ($K=$ `r unique(list_param[[2]]$k)`). We also varied relative fitness of captive-bred individuals ($f_R=$ `r unique(list_param[[2]]$phi)`) as this is a common interest in captive-breeding programs. Meanwhile, we fixed values of the following parameters: the number of species ($S=$ `r unique(list_param[[2]]$n_species)`), maximum intrinsic growth rate of unenhanced species ($r_{\text{max}}=$ `r unique(list_param[[2]]$r_max)`), and environmental stochasticity ($\sigma_{\varepsilon}=$ `r unique(list_param[[2]]$sd_env)`). We used $r_{\text{max}}=$ `r unique(list_param[[2]]$r_max)` because the intrinsic growth rate higher than this value was rarely observed in nature [@myersMaximumReproductiveRate1999]. This simulation setup resulted in `r nrow(list_param[[2]])` sets of parameter combinations.

@@

  cap[i] <- paste0("Theoretical predictions for the release effect in a ten-species community. Rows represent different response variables, and columns show distinct simulation scenarios with different strengths of interspecific competition ($\\bar{\\alpha}$) and relative fitness of captive-bred individuals ($f_R$). Lines are loess curves (mean) with shades indicating associated 95% confidence intervals. Other parameters are: ",
                       "number of species $S$ = ", df_param$n_species[i], "; intrinsic growth rate of an enhanced species $r_1$ = ", df_param$r1[i], "; maximum intrinsic growth rate of unenhanced species $r_{\\text{max}}$ = ", df_param$r_max[i], "; environmental stochasticity $\\sigma_{\\varepsilon}$ = ", df_param$sd_env[i], "; carrying capacity $K$ = ", df_param$k[i], ".")
